Current State of Knowledge Representation Systems for Robotics

### 2011-12-13 krs-survey.tex
Added a picture of the Brownie scenario, made in MORSE

\fxnote{Add nice illustrations from MORSE}

@@

We entitle our scenario ``the Brownie scenario''.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A typology of features of knowledge representation systems}
\label{sect|features}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{figs/brownie_scenario.jpg}
	\caption{A representation of the scenario, in the MORSE simulator}
	\label{fig|scenario}
\end{figure*}

@@

We entitle our scenario ``the Brownie scenario'' (Fig.~\ref{fig|scenario}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A typology of features of KRS for robotics}
\label{sect|features}
